Relative parabolic factorizations of Chevalley groups

### 2015-09-01 paper.tex
Several tabular and alignment issues

\subsection{Elementary subgroup}\label{sec:elementary}
Recall from~\cite{St78, VP} that for $\alpha\in \Phi$, $\xi\in R$ one can define certain elements $x_{\alpha}(\xi)$ of $\G_{sc}(\Phi, R)$ called {\it elementary root unipotents}.
These elements satisfy the well-known Steinberg relations:
\begin{align}
& \phantom{\left[{}\vphantom{x_\beta(t)}\right.}
x_\alpha(s) x_\alpha(t) = x_\alpha(s+t), \label{rel:add}\\
& \left[x_\alpha(s),  x_\beta(t)\right] = \prod x_{i\alpha + j\beta}\left(N_{\alpha\beta ij}\, s^i t^j\right),\quad \alpha\neq-\beta, \quad N_{\alpha\beta ij}\in\mathbb{Z}. \label{rel:CCF}
\end{align} 
The indices $i$, $j$ in the above formula range over all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
The integers $N_{\alpha\beta ij}$ are called {\it structure constants} of the Chevalley group $\G(\Phi,R)$ and depend only on $\Phi$.
We refer the reader to~\cite[\S14]{VP} for basic properties of structure constants.

@@

Define semisimple root elements $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$ as $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w_\alpha(-1)$.
The elements $h_\alpha(\varepsilon)$ satisfy the following relations:
\begin{align}
 [ h_\alpha(\varepsilon_1), h_\beta(\varepsilon_2)] & = 1, & \alpha, \beta \in \Phi,\ \varepsilon_1, \varepsilon_2 \in R^*  \label{rel:h-comm} \\
 h_\alpha(\varepsilon_1 \varepsilon_2) & = h_\alpha(\varepsilon_1) h_\alpha(\varepsilon_2) & \alpha \in \Phi,\ \varepsilon_1, \varepsilon_2 \in R^* \label{rel:h-mult} \\
 h_\alpha(\varepsilon)x_\beta(\xi)h_\alpha(\varepsilon)^{-1} & = x_\beta\left(\varepsilon^{\langle\beta,\alpha\rangle}\xi\right) & \alpha, \beta \in \Phi,\ \varepsilon \in R^*, \xi \in R \label{rel:h-w}
\end{align}

>>>>

\subsection{Elementary subgroup}\label{sec:elementary}
Recall from~\cite{St78, VP} that for $\alpha\in \Phi$, $\xi\in R$ one can define certain elements $x_{\alpha}(\xi)$ of $\G_{sc}(\Phi, R)$ called {\it elementary root unipotents}.
These elements satisfy the well-known Steinberg relations:
\begin{align}
& \phantom{[}
x_\alpha(s) x_\alpha(t) = x_\alpha(s+t), \label{rel:add}\\
& [x_\alpha(s),  x_\beta(t)] = \prod x_{i\alpha + j\beta}\left(N_{\alpha\beta ij}\, s^i t^j\right),\quad \alpha\neq-\beta, \quad N_{\alpha\beta ij}\in\mathbb{Z}. \label{rel:CCF}
\end{align} 
The indices $i$, $j$ in the above formula range over all positive natural numbers such that $i\alpha + j\beta\in\Phi$.
The integers $N_{\alpha\beta ij}$ are called {\it structure constants} of the Chevalley group $\G(\Phi,R)$ and depend only on $\Phi$.
We refer the reader to~\cite[\S14]{VP} for basic properties of structure constants.

@@

Define semisimple root elements $h_\alpha(\varepsilon)$, $\alpha\in\Phi$, $\varepsilon\in R^*$ as $h_\alpha(\varepsilon)=w_\alpha(\varepsilon)w_\alpha(-1)$.
The elements $h_\alpha(\varepsilon)$ satisfy the following relations:
\begin{alignat}{2}
& [ h_\alpha(\varepsilon_1), h_\beta(\varepsilon_2)] = 1, &\quad& \alpha, \beta \in \Phi,\ \varepsilon_1, \varepsilon_2 \in R^*; \label{rel:h-comm} \\
& \phantom{[} h_\alpha(\varepsilon_1 \varepsilon_2) = h_\alpha(\varepsilon_1) h_\alpha(\varepsilon_2), && \alpha \in \Phi,\ \varepsilon_1, \varepsilon_2 \in R^*; \label{rel:h-mult} \\
& \phantom{[} h_\alpha(\varepsilon)x_\beta(\xi)h_\alpha(\varepsilon)^{-1} = x_\beta\left(\varepsilon^{\langle\beta,\alpha\rangle}\xi\right), && \alpha, \beta \in \Phi,\ \varepsilon \in R^*, \xi \in R. \label{rel:h-w}
\end{alignat}
